FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-06-08 paper.tex
Minor restructure, talk about Inf

%% --- autogenerated TOC ---
% juliacon
% document
%   Introduction
%   To Kill a Floating Point
%     Where do NaNs come from?
%     NaN kills
%   FloatTracker Internals
%     Catching NaN kills
%     NaN propagation monitoring
%     NaN injection
%   Case Studies
%     Surprise NaNs: ShallowWaters
%     NaN fuzzing to find a kill: OrdinaryDiffEq
%     Finch
%     A Bug-Hunting Safari
%   Evaluation
%   Discussion
%     Tracking more than NaNs
%     Enhanced Fuzzing
%   Related Work
%   Acknowledgments
% document
%% --- end autogenerated TOC ---

@@

\section{To Kill a Floating Point}
% If anyone has a better "kill" pun/reference than "To Kill a Mockingbird", I'm all ears.
% I think we will definitely need a clear, detailed section on how NaNs crop up and how they can be killed.

@@

@@

% Yadda yadda yadda...

\subsection{NaN kills}

Most mathematical operations preserve NaNs.
However, there are some instances where NaNs can disappear, but not before potentially altering the correctness of the program!

% \begin{itemize}
% \item $x \; \texttt{cmp} \; y \rightarrow false$ where \texttt{cmp} is a binary comparison like \texttt{<}, \texttt{>}, \texttt{<=}, etc. and $x$ or $y$ is NaN.
% \item $1^{NaN} \rightarrow 1$
% \item $NaN^{0} \rightarrow 1$
% \end{itemize}

@@

% Yadda yadda yadda...

% What else do we need to talk about? What other problems do we need to set up so that FloatTracker's solutions are clear?

>>>>

%% --- autogenerated TOC ---
% juliacon
% document
%   Introduction
%     To Kill a Floating Point
%     FloatTracker
%   Floating Point Exception Primer
%     Where do NaNs come from?
%     Infinity
%   FloatTracker Internals
%     Catching NaN kills
%     NaN propagation monitoring
%     NaN injection
%   Case Studies
%     Surprise NaNs: ShallowWaters
%     NaN fuzzing to find a kill: OrdinaryDiffEq
%     Finch
%     A Bug-Hunting Safari
%   Evaluation
%   Discussion
%     Tracking more than NaNs
%     Enhanced Fuzzing
%   Related Work
%   Acknowledgments
% document
%% --- end autogenerated TOC ---

@@

% Here is a short, illustrative example about the problem.
\subsection{To Kill a Floating Point}
\label{s:to-kill-a-fp}
% If anyone has a better "kill" pun/reference than "To Kill a Mockingbird", I'm all ears.

@@

\subsection{FloatTracker}
% I'd love to find some Sherlock Holmes title for this section, as it would be a subtle nod to Sherlogs.jl and would be a nice literary reference to compliment "To Kill a Mockingbird"

\section{Floating Point Exception Primer}

In our work we focused on two of the most common problematic values in the floating point space: NaN and Inf.
We leave the possibility of tracking other kinds of troublesome values (e.g. subnormal numbers) open, but for our work we restrict ourselves to just these values.

@@

When one of these events happens, we call it a NaN \emph{generation}.

Most mathematical operations preserve NaNs.
We call these instances NaN \emph{propagation}, as the NaN is propagated from the source in the arguments to the result.

There are, however, some instances where the IEEE standard requires that NaNs to \emph{not} propagate from arguments to the result; we call these NaN \emph{kills}.
Sometimes this can be good---an \texttt{isnan} check should clearly return a boolean and not a NaN---but kills are often harmful in two ways:

\begin{enumerate}
  \item Users no longer see that there was some errant operation: NaNs are an opportunity to closely examine data for problems and code for unsoundness.
  \item NaN kills can influence the control of a program leading to incorrect results, as we saw in~\cref{to-kill-a-fp}.
\end{enumerate}

Here are cases where, according to the IEEE standard, a NaN can be killed:

@@

FloatTracker monitors these and all other operations for interesting events.

\subsection{Infinity}

There are two infinities, $+\infty$ and $-\infty$, but they behave the same for our purposes, so we will refer to them just as ``Inf''.
Like NaNs, Inf can crop up when bad math happens: $\frac{x}{0} \rightarrow \infty$ when $x \ne 0$.
Inf can also arise when numbers get too big or too small for the choice of representation.
